### 2023-03-01 cvpr_final_report/PaperForReview.tex
Initial report available for Chinese

% CVPR 2023 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)
\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
% \usepackage[review]{cvpr}      % To produce the REVIEW version
\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

\usepackage{CJKutf8} % For chinese output

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}
\begin{CJK*}{UTF8}{bsmi}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Fuck you for \confName~Proceedings}

\author{王浩 \\
國立成功大學　資訊工程學系\\
% First line of institution1 address\\
{\tt\small Howard.H.Wang.23@gmail.com}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
杜孟聰\\
國立成功大學　資訊工程學系\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
   The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section, must be no longer than eight pages in length.
The references section will not be included in the page count, and there is no limit on the length of the references section.
For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for \confName\ \confYear.}

Overlength papers will simply not be reviewed.
This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera-ready copy should not contain a ruler.
(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)

Reviewers:
note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.

\subsection{Paper ID}
Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.

\subsection{Mathematics}

Please number all of your sections and displayed equations as in these examples:
\begin{equation}
  E = m\cdot c^2
  \label{eq:important}
\end{equation}
and
\begin{equation}
  v = a\cdot t.
  \label{eq:also-important}
\end{equation}
It is important for readers to be able to refer to any particular equation.
Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
All authors will benefit from reading Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind review.
Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
That is all.
(But see below for tech reports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
it says that you are building on her work.
If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:
\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
Then submit the tech report as supplemental material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
solution.
The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.
Do not write ``We show how to improve our previous work [Anonymous, 1968].
This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors.
Instead write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.
   This system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
   Ours handles it by including a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
   It displayed the following behaviours, which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
For your results, however, you should not identify yourself and should not mention your participation in the challenge.
Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}

   \caption{Example of caption.
   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
   \label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a sentence-ending space.
So \eg is correct, {\em e.g.} is not.
The provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
However, use it only when there are three or more authors.
Thus, the following is correct:
   ``Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.

% Update the cvpr.cls to do the following automatically.
% For this citation style, keep multiple citations in numerical (not
% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
% \cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
  \centering
  \begin{subfigure}{0.68\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{An example of a subfigure.}
    \label{fig:short-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{Another example of a subfigure.}
    \label{fig:short-b}
  \end{subfigure}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}
\label{sec:formatting}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
The second and following pages should begin 1 inch (2.54 cm) from the top edge.
On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
high.
%
Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
The \LaTeX\ template takes care of this when used properly.

%-------------------------------------------------------------------------
\subsection{Type style and fonts}

Wherever Times is specified, Times Roman may also be used.
If neither is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE.
Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type.
This information is to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT.
Type main text in 10-point Times, single-spaced.
Do NOT use double-spacing.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Make sure your text is fully justified---that is, flush left and flush right.
Please do not place any additional blank lines between paragraphs.

Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-, second-, and third-order headings.

FIRST-ORDER HEADINGS.
(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS.
(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{Cross-references}

For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.

\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.
Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.

If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{CJK*}
\end{document}

### 2023-03-02 cvpr_final_report/PaperForReview.tex
Delete template context and write some basic part

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{\LaTeX\ Fuck you for \confName~Proceedings}
+\title{Google - Isolated Sign Language Recognition}
 
@@
 國立成功大學　資訊工程學系\\
-% First line of institution1 address\\
+F74082141\\
 {\tt\small Howard.H.Wang.23@gmail.com}
@@
 國立成功大學　資訊工程學系\\
-First line of institution2 address\\
+F74082028\\
 {\tt\small secondauthor@i2.org}
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
-   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
-   The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+   In this paper, we classify isolated American Sign Language (ASL) signs. We create a deep learning model trained on labeled landmark data extracted using the MediaPipe Holistic Solution.
 \end{abstract}
@@
 \label{sec:intro}
-
-Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
-This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.
+Around $90\%$ of which are born to hearing parents many of which may not know American Sign Language. 
+Without sign language, deaf babies are at risk of Language Deprivation Syndrome. 
+Learning American Sign Language takes time and resources, which many parents don't have.
+Training a sign language recognizer can improve the learning and confidence of parents who want to learn sign language to communicate with their loved ones.
 
 %-------------------------------------------------------------------------
-\subsection{Language}
+\subsection{American Sign Language}
 
-All manuscripts must be in English.
+American Sign Language (ASL) is a language used primarily by members of the Deaf community in North America. 
+It is not a visual representation of English, but has its own unique grammar, syntax, and vocabulary. 
+ASL is a visual-gestural language, meaning that it uses facial expressions, body language, and hand movements to convey meaning.
 
-\subsection{Dual submission}
+\subsection{Isolated Sign Language Recognition}
 
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a
-discussion of the policy on dual submissions.
+ISLR stands for Isolated Sign Language Recognition, 
+which is the process of recognizing sign language gestures performed by a person in isolation, 
+without considering the context or the surrounding gestures. 
+We will train a machine learning model that can accurately recognize isolated sign language signs and classify them into the correct sign category.
 
-\subsection{Paper length}
-Papers, excluding the references section, must be no longer than eight pages in length.
-The references section will not be included in the page count, and there is no limit on the length of the references section.
-For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for \confName\ \confYear.}
+%------------------------------------------------------------------------
+\section{System framwork}
+\label{sec:formatting}
 
-Overlength papers will simply not be reviewed.
-This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
-The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.
+We will use the raw data extraced from MediaPipe Holistic Solution which record every movement in video by landmark.
+Based on that data, we use ensamble model training a deep learning model for classifying isolated American Sign Language (ASL) signs.
 
 %-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
-The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
-If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera-ready copy should not contain a ruler.
-(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)
+\subsection{Data Type}
 
-Reviewers:
-note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.
-
-\subsection{Paper ID}
-Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
-If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations as in these examples:
-\begin{equation}
-  E = m\cdot c^2
-  \label{eq:important}
-\end{equation}
-and
-\begin{equation}
-  v = a\cdot t.
-  \label{eq:also-important}
-\end{equation}
-It is important for readers to be able to refer to any particular equation.
-Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
-It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
-(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
-All authors will benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind review.
-Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.
-
-Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
-That is all.
-(But see below for tech reports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
-it says that you are building on her work.
-If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
-In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
-For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
-Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
-Then submit the tech report as supplemental material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
-For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
-solution.
-The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.
-Do not write ``We show how to improve our previous work [Anonymous, 1968].
-This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors.
-Instead write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.
-   This system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
-   Ours handles it by including a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
-   It displayed the following behaviours, which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
-A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-  \centering
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-
-   \caption{Example of caption.
-   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
-   \label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a sentence-ending space.
-So \eg is correct, {\em e.g.} is not.
-The provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
-If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
-However, use it only when there are three or more authors.
-Thus, the following is correct:
-   ``Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.
-
-% Update the cvpr.cls to do the following automatically.
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}{0.68\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{An example of a subfigure.}
-    \label{fig:short-a}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.28\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Another example of a subfigure.}
-    \label{fig:short-b}
-  \end{subfigure}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
-\end{figure*}
+MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams. 
+The way that MediaPipe Holistic Solution record every movement of human face, body and hands is landmarks.
+Landmarks or keypoints are like dots that are placed on important areas of an object or a person's body. 
+These dots help a computer to understand where these important areas are and how they are moving.
 
 %------------------------------------------------------------------------
-\section{Formatting your paper}
-\label{sec:formatting}
-
-All text must be in a two-column format.
-The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
-The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
-The second and following pages should begin 1 inch (2.54 cm) from the top edge.
-On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
-for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
-high.
-%
-Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
-The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
-The \LaTeX\ template takes care of this when used properly.
-
-%-------------------------------------------------------------------------
-\subsection{Type style and fonts}
-
-Wherever Times is specified, Times Roman may also be used.
-If neither is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE.
-Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
-The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
-do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
-Leave two blank lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type.
-This information is to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT.
-Type main text in 10-point Times, single-spaced.
-Do NOT use double-spacing.
-All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
-Make sure your text is fully justified---that is, flush left and flush right.
-Please do not place any additional blank lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
-Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-, second-, and third-order headings.
-
-FIRST-ORDER HEADINGS.
-(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS.
-(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
-If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{Cross-references}
-
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
-\begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
-\end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
-Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
-Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.
-
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit your finished paper.
-We MUST have this form before your paper can be published in the proceedings.
-
-Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
-\url{https://www.computer.org/about/contact}.
+\section{Expected Result}
 
 %%%%%%%%% REFERENCES
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{egbib}
-}
+% {\small
+% \bibliographystyle{ieee_fullname}
+% \bibliography{egbib}
+% }
 

### 2023-03-02 cvpr_final_report/PaperForReview.tex
Add expected result

@@
 
-We will use the raw data extraced from MediaPipe Holistic Solution which record every movement in video by landmark.
+We will use the raw data extracted from MediaPipe Holistic Solution which record every movement in video by landmark.
 Based on that data, we use ensamble model training a deep learning model for classifying isolated American Sign Language (ASL) signs.
@@
 MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams. 
-The way that MediaPipe Holistic Solution record every movement of human face, body and hands is landmarks.
+The way that MediaPipe Holistic Solution record human of facial expressions, body language, and hand movements is landmarks.
 Landmarks or keypoints are like dots that are placed on important areas of an object or a person's body. 
@@
 %------------------------------------------------------------------------
+\subsection{Model}
+
+%------------------------------------------------------------------------
 \section{Expected Result}
+We hope creating the state-of-the-art model to predicted the American Sign Language (ASL) signs correctly
+with the input data of every video frame landmarks captured by MediaPipe Holistic Solution.
 

### 2023-03-03 cvpr_final_report/PaperForReview.tex
Add first citation

@@
 
-ISLR stands for Isolated Sign Language Recognition, 
-which is the process of recognizing sign language gestures performed by a person in isolation, 
+ISLR stands for Isolated Sign Language Recognition, which is the task of recognizing individual signs or tokens called glosses from a given segment of signing video clip.
+It is the process of recognizing sign language gestures performed by a person in isolation, 
 without considering the context or the surrounding gestures. 
@@
 
-MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams. 
+MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams~\cite{https://doi.org/10.48550/arxiv.1906.08172}.
 The way that MediaPipe Holistic Solution record human of facial expressions, body language, and hand movements is landmarks.
@@
 
-%%%%%%%%% REFERENCES
-% {\small
-% \bibliographystyle{ieee_fullname}
-% \bibliography{egbib}
-% }
+%%%%%%%% REFERENCES
+{\small
+\bibliographystyle{ieee_fullname}
+\bibliography{egbib}
+}
 

### 2023-03-03 cvpr_final_report/PaperForReview.tex
Add model descri and picture

@@
 \usepackage{booktabs}
+\graphicspath{ {./images/} }
 
@@
 ISLR stands for Isolated Sign Language Recognition, which is the task of recognizing individual signs or tokens called glosses from a given segment of signing video clip.
-It is the process of recognizing sign language gestures performed by a person in isolation, 
-without considering the context or the surrounding gestures. 
+It is the process of recognizing sign language gestures performed by a person in isolation, without considering the context or the surrounding gestures. 
 We will train a machine learning model that can accurately recognize isolated sign language signs and classify them into the correct sign category.
@@
 \subsection{Data Type}
-
-MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams~\cite{https://doi.org/10.48550/arxiv.1906.08172}.
-The way that MediaPipe Holistic Solution record human of facial expressions, body language, and hand movements is landmarks.
+\includegraphics[width=80mm]{holistic_pipeline_example}
+MediaPipe Holistic Solution~\cite{https://doi.org/10.48550/arxiv.1906.08172} is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams.
+The way that MediaPipe Holistic Solution record facial expressions, body language, and hand movements is landmarks.
 Landmarks or keypoints are like dots that are placed on important areas of an object or a person's body. 
@@
 \subsection{Model}
+First, we will use simple linear model with adding some activation functions to be our basic model.
+In order to get a better score, we would also tried to modified some input data fromat according to the properties of facial expressions, body language, and hand movements.
+\includegraphics[width=80mm]{ConvLSTM}
+We will also try some time-series model and convolution-based model such as ConvLSTM~\cite{NIPS2015_07563a3f} in order to find out the best model fitting the feature in our viddo-captured frame data.
 

### 2023-03-03 cvpr_final_report/PaperForReview.tex
Change wrong word

@@
 \section{Expected Result}
-We hope creating the state-of-the-art model to predicted the American Sign Language (ASL) signs correctly
+We hope creating the state-of-the-art model to predict the American Sign Language (ASL) signs correctly
 with the input data of every video frame landmarks captured by MediaPipe Holistic Solution.

### 2023-03-05 cvpr_final_report/PaperForReview.tex
Change expression way

--- 2023-03-03 cvpr_final_report/PaperForReview.tex
@@
 F74082028\\
-{\tt\small secondauthor@i2.org}
+{\tt\small F74082028@gs.ncku.edu.tw}
 }
@@
 \begin{abstract}
-   In this paper, we classify isolated American Sign Language (ASL) signs. We create a deep learning model trained on labeled landmark data extracted using the MediaPipe Holistic Solution.
+   This paper aims to classify isolated American Sign Language (ASL) signs using a deep learning model. 
+   To achieve this, we trained the model on labeled landmark data extracted via the MediaPipe Holistic Solution. 
+   Our approach leverages the accuracy and reliability of this technology to enhance the robustness of the model and improve its performance. 
+   By accurately classifying ASL signs, our method has the potential to support individuals with hearing impairments and 
+   enable better communication between hearing and non-hearing populations.
 \end{abstract}
@@
 \label{sec:intro}
-Around $90\%$ of which are born to hearing parents many of which may not know American Sign Language. 
-Without sign language, deaf babies are at risk of Language Deprivation Syndrome. 
-Learning American Sign Language takes time and resources, which many parents don't have.
-Training a sign language recognizer can improve the learning and confidence of parents who want to learn sign language to communicate with their loved ones.
+Deaf children born to hearing parents are at risk of Language Deprivation Syndrome if they don't have access to a fully developed language early in life. 
+However, learning American Sign Language (ASL) can be time-consuming and resource-intensive for parents. 
+Automatic sign language recognition technology can help overcome this barrier by recognizing and translating signs into text or speech.
+
+In this paper, we propose a novel approach to isolated sign language recognition using computer vision techniques and machine learning algorithms. 
+Our approach improves accuracy, robustness, and speed, as demonstrated on a publicly available dataset.
 
@@
 
-We will use the raw data extracted from MediaPipe Holistic Solution which record every movement in video by landmark.
-Based on that data, we use ensamble model training a deep learning model for classifying isolated American Sign Language (ASL) signs.
+We will use the raw data extracted from the MediaPipe Holistic Solution, which records every movement in video by landmark.
+Based on that data, we use an ensamble model to train a deep learning model for classifying isolated American Sign Language (ASL) signs.
 
@@
 \subsection{Data Type}
+MediaPipe Holistic Solution~\cite{https://doi.org/10.48550/arxiv.1906.08172} is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams.
+\includegraphics[width=80mm]{holistic_pipeline_example}
+The way that MediaPipe Holistic Solution records facial expressions, body language, and hand movements is by using landmarks.
 
-MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams~\cite{https://doi.org/10.48550/arxiv.1906.08172}.
-The way that MediaPipe Holistic Solution record human of facial expressions, body language, and hand movements is landmarks.
 Landmarks or keypoints are like dots that are placed on important areas of an object or a person's body. 
@@
 
+Our proposed model leverages a simple linear architecture with added activation functions to form 
+the foundation of our approach. To enhance the model's performance, we will modify the input data format, 
+taking into consideration the unique properties of facial expressions, body language, and hand movements.
+\includegraphics[width=80mm]{ConvLSTM}
+In addition, we will explore the use of time-series models and convolution-based models, 
+such as ConvLSTM~\cite{NIPS2015_07563a3f}, to identify the optimal model for fitting the features present in our video-captured frame data. 
+By evaluating multiple model architectures and comparing their effectiveness, 
+we aim to select the most robust and efficient approach for our isolated American Sign Language (ASL) sign recognition task.
+
+Our model development process is designed to enhance the accuracy and reliability of our approach, 
+thereby improving the overall quality of our results. 
+Through a comprehensive evaluation of various model architectures, we aim to establish a state-of-the-art ASL sign recognition system 
+that can effectively support communication between deaf and hearing populations.
+
 %------------------------------------------------------------------------
 \section{Expected Result}
-We hope creating the state-of-the-art model to predicted the American Sign Language (ASL) signs correctly
-with the input data of every video frame landmarks captured by MediaPipe Holistic Solution.
+Our proposed state-of-the-art model, which utilizes the input data of every video frame's landmarks captured by the MediaPipe Holistic Solution, 
+is expected to significantly improve the accuracy and speed of isolated sign language recognition. 
+We anticipate that the model will achieve high recognition rates for individual signs, 
+thus aiding in the communication and language acquisition process of individuals who are deaf or hard of hearing. 
+We believe that our research will contribute to the development of more sophisticated and efficient sign language recognition technology, 
+making communication more accessible for the Deaf community
 

### 2023-04-17 cvpr_final_report/PaperForReview.tex
Finish data analysis

@@
 \usepackage{booktabs}
+\usepackage{xcolor}
 \graphicspath{ {./images/} }
@@
 
+{\color{blue} this 
+is the test for change 
+color}
+
 %-------------------------------------------------------------------------
@@
 %------------------------------------------------------------------------
-\section{System framwork}
+\section{Explorative Data Analysis}
 \label{sec:formatting}
 
-We will use the raw data extracted from the MediaPipe Holistic Solution, which records every movement in video by landmark.
-Based on that data, we use an ensamble model to train a deep learning model for classifying isolated American Sign Language (ASL) signs.
-
 %-------------------------------------------------------------------------
-\subsection{Data Type}
+\subsection{Raw Data Format}
 MediaPipe Holistic Solution~\cite{https://doi.org/10.48550/arxiv.1906.08172} is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams.
@@
 %------------------------------------------------------------------------
-\subsection{Model}
+\subsection{Data Selection}
+{\color{blue} 
+The data utilized in this study was obtained from Mediapipe’s Holistic solution and contains landmarks from three categories: Face, Pose (body), and Hand.
+In accordance with established linguistic norms, movements below the chest are generally not utilized in sign language for conveying linguistic meanings, therefore, we will exclude landmarks from the hips down and retain only the relevant landmarks for Pose landmarks.
+Although facial expressions are not an integral part of signing, they can still play a role in identifying words that require the signer to point to parts of the face.
+Furthermore, facial expressions can provide subtle cues to differentiate between similar signs.
+Thus, we will utilize landmarks for the major features of the face: eyes, eyebrows, nose, and lips, and trim out the rest.
+Given the crucial role of hands in sign language, all Hand landmarks will be included in our training data.
+In summary, our model will be trained using landmarks from the arms, hands, and major facial features to recognize isolated signs.
+}
 
-Our proposed model leverages a simple linear architecture with added activation functions to form 
-the foundation of our approach. To enhance the model's performance, we will modify the input data format, 
-taking into consideration the unique properties of facial expressions, body language, and hand movements.
-\includegraphics[width=80mm]{ConvLSTM}
-In addition, we will explore the use of time-series models and convolution-based models, 
-such as ConvLSTM~\cite{NIPS2015_07563a3f}, to identify the optimal model for fitting the features present in our video-captured frame data. 
-By evaluating multiple model architectures and comparing their effectiveness, 
-we aim to select the most robust and efficient approach for our isolated American Sign Language (ASL) sign recognition task.
+%------------------------------------------------------------------------
+\subsection{Data Imputation}
+{\color{blue}
 
-Our model development process is designed to enhance the accuracy and reliability of our approach, 
-thereby improving the overall quality of our results. 
-Through a comprehensive evaluation of various model architectures, we aim to establish a state-of-the-art ASL sign recognition system 
-that can effectively support communication between deaf and hearing populations.
+As described in the competition’s guidelines, not all frames’ Hand data are complete. We have identified two categories with respect to the nature of the missed Hand data:
+The first category is where the hand rests idle below the waist.
+In sign language, there are signs that require only one hand to convey meaning.
+In such cases, the signer usually rests the other hand at their side, and the missed landmarks on this hand can be disregarded.
+The second category involves hands that are raised around the chest or face.
+A hand in these positions usually indicate that it is actively being used to sign.
+In such cases, certain techniques need to be employed to deal with these lost data.
+In cases where hand data is lost in some frames but not others, interpolation can be employed to fill the gaps.
+The reliability of this method may depend on the number of subtle movements between the frames and the size of the gaps.
+Alternatively, if the loss of hand data is too substantial (e.g., if no hand data exists across the entire clip), discarding the clip altogether may be the best option.
+Another viable approach to imputing missed data is to use statistical methods such as averaging measures from other data with the same label.
+However, complications may arise when the number of frames differs across clips, even when they correspond to the same sign.
+
+}
+
+%------------------------------------------------------------------------
+
+\section{Input Data Format}
+\label{sec:formatting}
+
+%-------------------------------------------------------------------------
+
+\subsection{Hierarchical Encoding}
+{\color{blue} 
+Rather than plotting all landmarks on a shared “global” coordinate system, we will map landmarks onto a hierarchy of local coordinate systems based on the articulation of joints and muscles.
+We propose that organizing landmark coordinates in a hierarchical structure may help reduce the impact of variations in different realizations of the same sign.
+Hypothesis 1. Organizing landmark coordinates in a hierarchical structure in a gesture recognition task can help reduce the impact of variations in different realizations of the same sign.
+The reasoning to Hypothesis 1.
+is that, for most signs, it does not matter whether the hands are slightly below the chest or above it nor does it matter whether it is slightly outside of shoulder width or slightly within, i.e.
+slight variations in the relative position does not typically result in significant semantic differences.
+Such variations may be observed across differnt signers with differnt body structures and even in the same signer across different instances and, with one global coordinate system, are reflected systematically on all landmark coordinates of the hands.
+If we instead encode the hand landmarks in the wrists coordinate system, that variation will be eliminated in the hands and only reflected in the wrists and elbows.
+Since the number of landmarks impacted by this variation significantly decreases in the hierarchical scheme, we assert that this will in general make the model more robust to variations that are not semantically significant.
+}
+\includegraphics[width=80mm]{hierarchical_scheme}
+
+%------------------------------------------------------------------------
+
+\subsection{Orientation-Focused Encoding}
+{\color{blue} 
+On top of mapping landmarks onto a hierarchy of coordinate systems, we aim to investigate the impact of an extra encoding scheme on the performance of the model.
+Specifically, we will explore the effect of encoding only the orientation of landmarks with respect to their origin (i.e., parent) on the final results.
+To achieve this, we will scale all landmarks down to a uniform size.
+On one hand, this approach may help eliminate slight variations in landmark coordinates that arise from individual differences in body structure, such as differences in bone length.
+On the other hand, since only the x and y coordinates are used in this specific implementation, rotations that do not result in a change in orientation on the xy plane may not be reliably captured.
+In contrast, if the norm or length of the landmark vectors is also encoded, at least some information about the degree of rotation could be partially captured.
+For example, the shorter the forearm appears, the more it has rotated towards the observer.
+}
+
+%------------------------------------------------------------------------
+\subsection{Temporal Normalization by Down-/Upsampling}
+{\color{blue} 
+Accounting for the different signing speeds among individuals is an important consideration in training a robust sign language recognition model.
+In practice, signers can vary greatly in their signing speed, and this can result in variations in the rate at which landmarks move from frame to frame.
+To ensure that our model is not overly sensitive to such differences, we will downsample or upsample the clips to achieve a uniform number of frames.
+By doing so, we can eliminate any potential errors introduced by variations in the speed at which landmarks move.
+}
+%------------------------------------------------------------------------
+
+\subsection{Landmark Mirroring}
+{\color{blue} 
+In sign language, signers commonly rely on a dominant hand to perform the majority of signs, with the specific hand varying among individuals.~\cite{Sign} When signing words that require only one hand, signers typically have the freedom to choose which hand to use.
+For words that require both hands and involve asymmetric movements, instructions usually designate separate sets of movements for the dominant hand and for the non-dominant hand; it is ultimately up to the signer to decide which hand is dominant.
+
+Thus, for most sign language gestures, flipping the gesture horizontally does not alter its meaning.
+We have thoroughly examined the dataset and identified no labels such as “left” or “right” for which the choice of dominant hand may affect the meaning.
+We have thus eliminated concerns for the impact of hand selection in this specific dataset; with that in mind, in our implementation, we will augment the dataset by creating a mirrored version of each clip, enabling the model to learn to recognize the gesture regardless of which hand is designated as dominant.
+}
+%=========here i am ~~~
+%------------------------------------------------------------------------
+
+\section{Model}
+{\color{blue}
+The Transformer architecture has demonstrated efficacy in sequence-based tasks for dynamic gesture recognition~\cite{TR}.
+It is important to note that our task differs from the task described in~\cite{TR}, as our input data is comprised of landmark coordinates rather than bitmap images.
+Specifically, the authors in~\cite{TR} utilize a Convolutional Neural Network (CNN) architecture, ResNet-18, to convert bitmap images into embeddings before feeding them into the Transformer.
+Despite this difference, we find the Transformer architecture to be a suitable model for our task given its success in a similar domain.
+Our proposed implementation will use the Transformer with sequences of landmark coordinates as input, and the model will output probabilities for each label.
+
+Our proposed model will consist of a Transformer encoder, followed by a multi-layer perceptron (MLP) decoder.
+The encoder will be responsible for encoding the input sequence of landmark coordinates into a fixed-length representation, which will then be passed to the decoder to produce the final output probabilities for each label.
+The MLP decoder will consist of two fully connected layers with ReLU activation functions and a final softmax layer to produce the output probabilities.
+
+To improve the model’s ability to capture temporal dependencies between landmarks, we will also experiment with the use of a Recurrent Neural Network (RNN) architecture as an alternative to the Transformer encoder.
+In particular, we will explore the use of a Long Short-Term Memory (LSTM) network, which has been shown to be effective in capturing long-term dependencies in sequential data.
+}
 

### 2023-06-17 cvpr_final_report/PaperForReview.tex
Add learn relative pos and Integration info

@@
 Our approach improves accuracy, robustness, and speed, as demonstrated on a publicly available dataset.
-
-{\color{blue} this 
-is the test for change 
-color}
-
 %-------------------------------------------------------------------------
@@
 }
+%------------------------------------------------------------------------
+\section{Learning Relative Positions}
+In the realm of sign language recognition, the ability to discern relative positions between the hands and other parts of the body is of paramount importance.
+This becomes particularly evident in situations where the signer points to specific body parts.
+Moreover, the relative positions between different landmarks of the hands can also significantly influence the recognition process, especially in signs that necessitate the signer to tap one fingertip to another.
+These relative positions can provide crucial information that aids the recognizer in accurately interpreting the signs.
+In this exploration, we ask ourselves the question of whether a model can independently learn to identify relevant relative positions, given the raw landmark points.
+The aim is to ascertain whether it is possible to eliminate the need to supply the model with programmatically calculated and selected relative positions between pairs of landmark points, without compromising the accuracy of recognition.
+
+A significant trade-off is evident in this scenario. The number of relative positions among 
+$n$
+ points is calculated as 
+$\frac{nx(n-1)}{2}$
+, which has a complexity of 
+$O(n^2)$
+.
+This could considerably increase the computational complexity during inference and backpropagation.
+Conversely, if explicit relative positions are entirely omitted in the inputs, the model will be compelled to learn them independently, if at all.
+This might prolong the time required for convergence.
+
+To better understand this trade-off, we propose two distinct approaches for training the sign language recognizer.
+%------------------------------------------------------------------------
+\subsection{Entrusting the Model with Extraction of Useful Relative Positions}
+In the first approach, we identify a set of landmarks, which include keypoints from the eyes, nose, lips, and the hand.
+We refer to this set as an ‘anchor group’.
+These keypoints are then fed into a frame-wise multi-level perceptron (MLP) layer.
+The underlying hypothesis here is that the MLP can learn to extract useful relative positions between these keypoints in each frame and subsequently utilize them for recognition.
+%------------------------------------------------------------------------
+\subsection{Explicit Computation of Relative Positions}
+The second approach takes a more direct route.
+Rather than entrusting the model with the task of extracting useful relative positions, we compute these positions explicitly in a feature expansion layer.
+In this scenario, the model’s primary task is to identify which relative positions are useful, without the added burden of having to extract them.
+%------------------------------------------------------------------------
+\section{Early Integration vs Late Integration}
+Inspired by the dichotomy between early and late fusion strategies in multi-modal learning as delineated in ~\cite{Boulahia2021}, our study delves into a similar contrast between early integration and late integration of different “feature groups” in the context of sign language recognition.
+%------------------------------------------------------------------------
+\subsection{Feature Grouping: Distinguishing Between Learning Shapes and Spatial Relations}
+In our approach, we categorize sets of landmark points into distinct groups, each of which serves a unique purpose.
+These groups can be broadly classified into three types: “local groups”, “anchor groups”, and the “difference group”.
+
+“Local groups” refer to groups that represent specific body parts, such as the hand, lips, etc.
+The primary objective of these groups is to enable the model to learn the “shape” of the corresponding body parts.
+
+“Anchor groups”, which are already introduced in the last section, are groups of keypoints from different body parts, designed to facilitate the learning of relative positions.
+
+Lastly, the “difference group” is a selected collection of computed differences (relative positions) between landmark points.
+
+The role of “anchor groups” or the “difference group” is to allow the model to learn the “spatial relations” between different body parts or landmarks.
+
+In our model, irrespective of the scheme we choose to adopt, all features of the same group are initially fed into a Multi-Layer Perceptron (MLP) to obtain a group-level representation.
+Integration, in this context, refers to the amalgamation of different group-level representations into a single, unified embedding.
+This integration could occur either before or after the transformer layer, i.e., early if before and late if after.
+Furthermore, this integration could involve any number of groups and could be between groups of the same type or of different types.
+In our exploration, we specifically focus on one particular variety of integration at two different stages; namely, we investigate how integrating “shape” and “spatial relations” information at different stages of the model affects performance.
 
 %------------------------------------------------------------------------
-\section{Expected Result}
-Our proposed state-of-the-art model, which utilizes the input data of every video frame's landmarks captured by the MediaPipe Holistic Solution, 
-is expected to significantly improve the accuracy and speed of isolated sign language recognition. 
-We anticipate that the model will achieve high recognition rates for individual signs, 
+\subsection{Early Integration: A Unified Approach}
+In the early integration approach, at the frame level, information from all different feature groups is consolidated into a single vector before the transformer attempts to learn how this unified representation evolves over time by comparing the frames.
+This scheme necessitates only one unifying transformer, and the final MLP classifier solely takes the output from this single transformer as input.
+\includegraphics[width=80mm]{early_integration.drawio}
+%------------------------------------------------------------------------
+\subsection{Late Integration: A Multi-Transformer Approach}
+Contrarily, in the late integration approach, information from different group types is represented as separate embeddings at the frame level.
+This necessitates multiple transformers, one for the “shape” embeddings and another for the “spatial relations” embeddings, to process how these two types of information change along the temporal dimension.
+Finally, the output embeddings from each transformer are combined before being fed into the final MLP classifier.
+\includegraphics[width=80mm]{late_integration.drawio}
+%------------------------------------------------------------------------
+\section{Result}
+Our model, which utilizes the input data of every video frame's landmarks captured by the MediaPipe Holistic Solution, 
+gets the accuracy $0.73$ of isolated sign language recognition.
+The parameters of our model are Early Integration with Anchor Group and final layer of model for dimension is $512$. Futhermore, the best score on Kaggle is $0.89$.
+We have done that the model will achieve high recognition rates for individual signs, 
 thus aiding in the communication and language acquisition process of individuals who are deaf or hard of hearing. 
 We believe that our research will contribute to the development of more sophisticated and efficient sign language recognition technology, 
-making communication more accessible for the Deaf community
+making communication more accessible for the Deaf community.
+%------------------------------------------------------------------------
 
